---
output: github_document
---

why should they use
how should they use
how do they get it

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dynUGENE

<!-- badges: start -->
<!-- badges: end -->

dynUGENE is an R package for the inference, simulation, and visualization of gene regulatory network dynamics from time-series expression data.

## Description

Purpose, how it add/improves current work, uniqueness

## Installation

<!-- You can install the released version of dynUGENE from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("dynUGENE") -->
<!-- ``` -->

Install the development version with:

``` r
install.packages("devtools")
devtools::install_github("tianyu-lu/dynUGENE", build_vignettes = TRUE)
library("dynUGENE")
```

## Overview

```{r Overview}
#ls(package:dynUGENE)
#data(package="dynUGENE")
```

For detailed tutorials, see the vignette here:

```{r Vignette}
browseVignettes("dynUGENE")
```

## Contributions

describe them, how it builds off of existing functions, which parts are yours

## References



## Acknowledgements

This package was developed as part of an assessment for 2020 BCB410H: Applied Bioinformatics, University of Toronto, Toronto, CANADA.

## Example

Load and do inference with repressilator data:

```{r example}
library(dynUGENE)
## load repressilator dataset

## infer network

## visualize inferred network

## simulate the inferred network dynamics

```


